### 2022-05-30 main/chapter_2ljets.tex
figure caption improvements

\begin{singlespacing}
\chapter{A search for new phenomena}
\label{chapter:2ljets}
%
\begin{epigraphs}
\qitem{%
An experiment is never a failure solely because it fails to
achieve predicted results. An experiment is a failure only when it also
fails adequately to test the hypothesis in question, when the data it
produces don’t prove anything one way or another.%
}%
{Robert~M.~Pirsig,
\textit{Zen and the Art of Motorcycle Maintenance},
1974~\cite{pirsig1999zen}}
\qitem{%
But there is one feature I notice that is generally missing in cargo cult
science. \ldots\
% That is the idea that we all hope you have learned in studying science in
% school--we never say explicitly what this is, but just hope that you catch
% on by all the examples of scientific investigation. It is interesting,
% therefore, to bring it out now and speak of it explicitly.
It's a kind of scientific integrity, a principle of scientific thought that
corresponds to a kind of utter honesty --- a kind of leaning over backwards.%
}%
{Richard~Feynman,
\textit{Cargo Cult Science},
1974~\cite{feynman1974cargo}}
\end{epigraphs}
\end{singlespacing}

@@

\begin{figure}[t]
\centering
\begin{subfigure}{0.48\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figures/2ljets_c1n2_llqqn1n1_wz.pdf}
    \caption{C1N2}
\end{subfigure}
\hfill
\begin{subfigure}{0.45\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figures/2ljets_n1n1_hhggzz.pdf}
    \caption{GMSB}
\end{subfigure}
\caption{%
Supersymmetric signal processes in the $\twoljets$-electroweak
analysis.
\textit{Figures reproduced from the paper%
}~\cite{atlas2022searches, atlas_susy_feynman}.
\\[0.5em]
Left: C1N2, where the initial $\chargino_1\textrm{--}\neutralino_2$ pair
is produced through a $s$-channel $W^{\pm}$ resonance and the masses of
weak bosons in decays are bounded by the mass splitting
$m(\chargino_1, \neutralino_2) - m(\neutralino_1)$.
We explore the parameters
$m(\chargino_1, \neutralino_2)$ and $m(\neutralino_1)$.
\\[0.5em]
Right: GMSB, where the initial $\neutralino_1\textrm{--}\neutralino_1$ pair
is produced by soft decays from pairs including $\chargino_1$,
$\neutralino_2$ or $\neutralino_1$.
Although the $h$ and $Z$ bosons decay to many states, we target
$Z\rightarrow \ell\ell$ with
$h/Z\rightarrow bb/jj$.
We explore the parameters
$m(\neutralino_1)$ and $B(\neutralino_1 \rightarrow h \tilde{G})$ with fixed
$m(\chargino_1, \neutralino_2) - m(\neutralino_1) = 1\,\eV[G]$.
}
\label{fig:2ljets_signal_diagrams}
\end{figure}

@@

\begin{figure}[tp]
\centering
\includegraphics[width=0.9\textwidth]{figures/2ljets_rjr_trees.pdf}
\caption{%
Decay trees for the $\twoljets$-RJR analysis~\cite{atlas2022searches}.
Both diagrams represent processes also targetted in the electroweak analysis.
(left) A fully-resolved decay tree with its particles labelled.
(right) Only the $Z\rightarrow\ell\ell$ (\underline{V}ector boson)
is resolved, but the supersymmetric system recoils off
hard QCD jets labelled ``ISR'', boosting the \underline{I}nvisible particles,
to generate visibly large $\met$ in models with small mass-splittings.
The same approach is used for SR-OffShell selections in the electroweak
analysis.
\emph{This figure was made by the RJR team.}
}
\label{fig:2ljets_rjr_decay_trees}
\end{figure}

@@

\begin{figure}[tp]
\centering
\begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figures/2ljets_rjr_23l_2l_summary.png}
    \caption{$2\ell$ RJR~\cite{atlas_rjr_23l_SUSY_2017_03}}
\end{subfigure}
\hfill
\begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figures/2ljets_rjr_23l_3l_summary.png}
    \caption{$3\ell$ RJR~\cite{atlas_rjr_23l_SUSY_2017_03}}
\end{subfigure}
\\[0.5em]
\begin{subfigure}{0.8\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figures/2ljets_rjr_summary_log.pdf}
    \caption{$\twoljets$-RJR~\cite{atlas2022searches}}
\end{subfigure}
\caption{%
Summary plots for RJR analyses:
(a) and (b)~two- and three- lepton selections respectively reproduced
from~\cite{atlas_rjr_23l_SUSY_2017_03},
(c)~all regions from the $\twoljets$-RJR search~\cite{atlas2022searches}.
Note the excesses in
$\mathrm{SR}2\ell\_\mathrm{Low}$ and $\mathrm{SR}2\ell\_\mathrm{ISR}$ of (a),
and in
$\mathrm{SR}3\ell\_\mathrm{Low}$ and $\mathrm{SR}3\ell\_\mathrm{ISR}$ of (b).
\textit{Sub-figure (c) was made by the RJR team.}
}
\label{fig:2ljets_rjr_summaries}
\end{figure}

@@

% signal models
\begin{figure}[tp]
\centering
\begin{subfigure}{0.45\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figures/2ljets_strong_gogo_qqqqllllN1N1_N2.pdf}
    \caption{gluino-slepton}
\end{subfigure}
\hfill
\begin{subfigure}{0.47\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figures/2ljets_strong_gogo_qqqqZZN1N1.pdf}
    \caption{gluino-$Z^{(*)}$}
\end{subfigure}
\\[0.5em]
\begin{subfigure}{0.45\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figures/2ljets_strong_sqsq_qqZZN1N1.pdf}
    \caption{squark-$Z^{(*)}$}
\end{subfigure}
\caption{%
Supersymmetric signal processes in the $\twoljets$-strong search.
\textit{Figures reproduced from the paper%
}~\cite{atlas2022searches, atlas_susy_feynman}.
\\[0.5em]
\TODO{expand}
}
\label{fig:2ljets_strong_signal_diagrams}
\end{figure}

% exclusion plots
\begin{figure}[tp]
\centering
\begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figures/2ljets_strong_contours_gluino_slepton.pdf}
    \caption{gluino-slepton}
\end{subfigure}
\hfill
\begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figures/2ljets_strong_contours_gluino_z.pdf}
    \caption{gluino-$Z^{(*)}$}
\end{subfigure}
\\[0.5em]
\begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figures/2ljets_strong_contours_squark_z.pdf}
    \caption{squark-$Z^{(*)}$}
\end{subfigure}
\caption{%
Contours for signal models of the $\twoljets$-strong search.
\textit{Figures reproduced from the paper%
}~\cite{atlas2022searches}.
\\[0.5em]
\TODO{expand}
}
\label{fig:2ljets_strong_contours}
\end{figure}

@@

The benefit of an additional trigger could be in increased signal yields if
that trigger do not also harmfully increase inseparable backgrounds.
A study, \textit{which was performed by Knut Vadla}, investigated the effects
of of including one-lepton triggers.
In a signal-region-like selection requiring two leptons, two jets and
$\met > 200\,\eV[G]$, this study showed that two-lepton triggers already accept
in excess of $90\%$ of events from benchmark C1N2 models.
Therefore, any additional trigger has at most a $\approx10\%$;
improvement. Adding one-lepton triggers was found to increase efficiency by
only a few percentage points, depending on the model.
We considered that to be too little to be worthwhile.

>>>>

\begin{singlespacing}
\chapter{A search for new phenomena}
\label{chapter:2ljets}
%
\begin{epigraphs}
\qitem{%
An experiment is never a failure solely because it fails to
achieve predicted results. An experiment is a failure only when it also
fails adequately to test the hypothesis in question, when the data it
produces don’t prove anything one way or another.%
}%
{Robert~M.~Pirsig,
\emph{Zen and the Art of Motorcycle Maintenance},
1974~\cite{pirsig1999zen}}
\qitem{%
But there is one feature I notice that is generally missing in cargo cult
science. \ldots\
% That is the idea that we all hope you have learned in studying science in
% school--we never say explicitly what this is, but just hope that you catch
% on by all the examples of scientific investigation. It is interesting,
% therefore, to bring it out now and speak of it explicitly.
It's a kind of scientific integrity, a principle of scientific thought that
corresponds to a kind of utter honesty --- a kind of leaning over backwards.%
}%
{Richard~Feynman,
\emph{Cargo Cult Science},
1974~\cite{feynman1974cargo}}
\end{epigraphs}
\end{singlespacing}

@@

\begin{figure}[t]
\centering
\begin{subfigure}{0.48\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figures/2ljets_c1n2_llqqn1n1_wz.pdf}
    \caption{C1N2}
\end{subfigure}
\hfill
\begin{subfigure}{0.45\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figures/2ljets_n1n1_hhggzz.pdf}
    \caption{GMSB}
\end{subfigure}
\caption{%
Supersymmetric signal processes in the $\twoljets$-electroweak
analysis.
\emph{Figures are reproduced from the paper%
}~\cite{atlas2022searches, atlas_susy_feynman}.
\\[0.5em]
(a): C1N2, where the initial $\chargino_1\textrm{--}\neutralino_2$ pair
is produced through a $s$-channel $W^{\pm}$ resonance and the masses of
weak bosons in decays are bounded by the mass splitting
$m(\chargino_1, \neutralino_2) - m(\neutralino_1)$.
We explore the parameters
$m(\chargino_1, \neutralino_2)$ and $m(\neutralino_1)$.
\\[0.5em]
(b): GMSB, where the initial $\neutralino_1\textrm{--}\neutralino_1$ pair
is produced by soft decays from pairs including $\chargino_1$,
$\neutralino_2$ or $\neutralino_1$.
Although the $h$ and $Z$ bosons decay to many states, we target
$Z\rightarrow \ell\ell$ with
$h/Z\rightarrow bb/jj$.
We explore the parameters
$m(\neutralino_1)$ and $B(\neutralino_1 \rightarrow h \tilde{G})$ with fixed
$m(\chargino_1, \neutralino_2) - m(\neutralino_1) = 1\,\eV[G]$.
}
\label{fig:2ljets_signal_diagrams}
\end{figure}

@@

\begin{figure}[tp]
\centering
\includegraphics[width=0.9\textwidth]{figures/2ljets_rjr_trees.pdf}
\caption{%
Decay trees for the $\twoljets$-RJR analysis.
\emph{This figure was made by the RJR team.}~\cite{atlas2022searches}.
Both diagrams represent processes also targetted in the electroweak analysis.
(left) A fully-resolved decay tree with its particles labelled.
(right) Only the $Z\rightarrow\ell\ell$ (\underline{V}ector boson)
is resolved, but the supersymmetric system recoils off
hard QCD jets labelled ``ISR'', boosting the \underline{I}nvisible particles,
to generate visibly large $\met$ in models with small mass-splittings.
The same approach is used for SR-OffShell selections in the electroweak
analysis.
}
\label{fig:2ljets_rjr_decay_trees}
\end{figure}

@@

\begin{figure}[tp]
\centering
\begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figures/2ljets_rjr_23l_2l_summary.png}
    \caption{$2\ell$ RJR~\cite{atlas_rjr_23l_SUSY_2017_03}}
\end{subfigure}
\hfill
\begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figures/2ljets_rjr_23l_3l_summary.png}
    \caption{$3\ell$ RJR~\cite{atlas_rjr_23l_SUSY_2017_03}}
\end{subfigure}
\\[0.5em]
\begin{subfigure}{0.8\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figures/2ljets_rjr_summary_log.pdf}
    \caption{$\twoljets$-RJR~\cite{atlas2022searches}}
\end{subfigure}
\caption{%
Summary plots for RJR analyses:
(a) and (b)~two- and three- lepton selections respectively,
\emph{reproduced from}~\cite{atlas_rjr_23l_SUSY_2017_03},
(c)~all regions from the $\twoljets$-RJR search~\cite{atlas2022searches}.
Note the excesses in
$\mathrm{SR}2\ell\_\mathrm{Low}$ and $\mathrm{SR}2\ell\_\mathrm{ISR}$ of (a),
and in
$\mathrm{SR}3\ell\_\mathrm{Low}$ and $\mathrm{SR}3\ell\_\mathrm{ISR}$ of (b).
\emph{Sub-figure (c) was made by the RJR team.}
}
\label{fig:2ljets_rjr_summaries}
\end{figure}

@@

% signal models
\begin{figure}[tp]
\centering
\begin{subfigure}{0.45\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figures/2ljets_strong_gogo_qqqqllllN1N1_N2.pdf}
    \caption{gluino-slepton}
\end{subfigure}
\hfill
\begin{subfigure}{0.47\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figures/2ljets_strong_gogo_qqqqZZN1N1.pdf}
    \caption{gluino-$Z^{(*)}$}
\end{subfigure}
\\[0.5em]
\begin{subfigure}{0.45\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figures/2ljets_strong_sqsq_qqZZN1N1.pdf}
    \caption{squark-$Z^{(*)}$}
\end{subfigure}
\caption{%
Supersymmetric signal processes in the $\twoljets$-strong search.
\emph{Figures reproduced from the paper%
}~\cite{atlas2022searches, atlas_susy_feynman}.
\\[0.5em]
All models produce same-flavour, opposite-sign lepton pairs along with jets
and $\met$.
The gluino-slepton model (a) has a kinematic endpoint in $\mll$
given in Equation~\ref{eqn:2ljets_strong_max_mll}.
The gluino-$Z^{(*)}$ and squark-$Z^{(*)}$ models decay via $Z$ boson
resonances, which may be forced off-shell for small mass splittings
$m(\neutralino_2) - m(\neutralino_1) < m(Z)$.
}
\label{fig:2ljets_strong_signal_diagrams}
\end{figure}

% exclusion plots
\begin{figure}[tp]
\centering
\begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figures/2ljets_strong_contours_gluino_slepton.pdf}
    \caption{gluino-slepton}
\end{subfigure}
\hfill
\begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figures/2ljets_strong_contours_gluino_z.pdf}
    \caption{gluino-$Z^{(*)}$}
\end{subfigure}
\\[0.5em]
\begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figures/2ljets_strong_contours_squark_z.pdf}
    \caption{squark-$Z^{(*)}$}
\end{subfigure}
\caption{%
Contours for signal models of the $\twoljets$-strong search.
\emph{Figures were produced by the strong team%
}~\cite{atlas2022searches}.
\\[0.5em]
\TODO{expand}
}
\label{fig:2ljets_strong_contours}
\end{figure}

@@

The benefit of an additional trigger could be in increased signal yields if
that trigger do not also harmfully increase inseparable backgrounds.
A study, \emph{which was performed by Knut Vadla}, investigated the effects
of of including one-lepton triggers.
In a signal-region-like selection requiring two leptons, two jets and
$\met > 200\,\eV[G]$, this study showed that two-lepton triggers already accept
in excess of $90\%$ of events from benchmark C1N2 models.
Therefore, any additional trigger has at most a $\approx10\%$;
improvement. Adding one-lepton triggers was found to increase efficiency by
only a few percentage points, depending on the model.
We considered that to be too little to be worthwhile.
